%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------

  %---------------------------------------------------------
  %   \cventry
  %     {Undergraduate Internship} % Job title
  %     {Arak Oil refinery} % Organization
  %     {Arak, Iran} % Location
  %     {Jun. 2011 - Dec. 2013} % Date(s)
  %     {
  %       \begin{cvitems} % Description(s) of tasks/responsibilities
  %         \item {Working in different parts of QC lab}
  %       \end{cvitems}
  %     }
  \cventry
    {Senior Data Engineer}
    {Arcturis Data Ltd}
    {Kidlington, UK}
    {Nov. 2023 --- Present}
    Arcturis curates precision real-world data to support the development of new medicines. I joined in the
    early stages of the establishment of the Engineering department and played a pivotal role in the
    consolidation of the legacy infrastructure, greenfield build and migration to a replacement platform, and
    the operation of that platform in a maturing business landscape.
    {
      \begin{cvitems}
        \item{
          Developed vision and roadmap for core data pipeline including immediate risk mitigations.
          Executed on said roadmap, realising significantly better test coverage, reduction in development
          overhead and defect rate, and ultimately a processing time reduction from days to hours for typical
          operations.
        }
        \item{
          Architected and built greenfield AWS Organisation following best practices. Successfully completed
          whole-company migration from Azure tenant to AWS realising an approx. 50\% reduction in cloud
          expenditure on like-for-like infrastructure alone.
        }
        \item{
          Developed SOPs and software for company operations in federated data environments (NHS SDEs)
          and contributed to policy development as the company QMS was established.
        }
        \item{
          Planned and delivered end-user and stakeholder workshops to shape Engineering roadmap.
        }
        \item{
          Served as the company’s principal point of expertise for Python development.
        }
        \item{
          Significantly contributed to or wholly authored, deployed and owned multiple internal web
          applications; many of which were powered by LLM, and one such described in a published
          whitepaper which I co-authored in Frontiers in Digital Health.
        }
      \end{cvitems}
  }
  \cventry
    {Software Engineer II}
    {Iotic Labs Ltd (IOTICS)}
    {Remote, UK}
    {Jun. 2022 --- Nov. 2023}
    IOTICS was a startup leveraging the semantic web to solve interoperability challenges and apply FAIR data
    principles to allow cooperative data ecosystems to form. I was employed as a Software Engineer, developing
    the Core software that leveraged IoT, blockchain-inspired cryptography, a custom transport layer and cloud-
    decoupled architecture.
    {
      \begin{cvitems}
      \item{Implemented and reviewed complex features across core service stack primarily in Python and Golang, with some Rust components, including both REST and gRPC APIs.}
      \item{Re-implemented end-to-end CI/CD workflow including code architecture refactoring.}
      \item{Rearchitected product deployment, realising an overall 50+\% reduction in hosting costs.}
      \item{Provided post-sales end-to-end solution design and implementation for customer engagements.}
      \item{Delivered on-site technical product training for clients.}
      \item{Maintenance of core AWS architecture including load balancers/ASGs, VPC, DNS, ACM, IAM, etc.}
      \item{Administered applications such as JIRA/Confluence, GitHub, Okta, JFrog Platform}
      \item{Designed and delivered a prototype Azure-hosted product deployment for a prospective enterprise customer demo on a one-week turnaround.}
      \end{cvitems}
    }
  \cventry
    {Technology Associate/Software Engineer II-IV}
    {Elsevier Ltd}
    {Kidlington, UK}
    {Sep. 2019 --- Jun 2022}
    Elsevier Ltd is a major global scientific, technical, and medical information provider, part of the RELX Group.
    Working within the Business Technology Solutions division, I joined as a Technology Associate and was
    promoted three times to Software Engineer IV during my employment.
    {
      \begin{cvitems}
      \item{Led development in critical data warehouse migration to Snowflake + AWS, with projected \$2m annual reduction in software/infrastructure costs and over 50\% reduction in daily data processing time.}
      \item{Designed and implemented of PySpark-based cross-database reconciliation framework and other Python-based data testing utilities.}
      \item{Developed and maintained ELT pipelines for multiple financial data warehouses using Oracle/OBIEE, Oracle PL/SQL and Talend.}
      \item{Linux server administration of internal Tableau Server, including upgrade and change management and acting as L1-3 support.}
      \end{cvitems}
    }


  %---------------------------------------------------------
\end{cventries}
% \clearpage
